Off the beaten path: \\ Gaia reveals GD-1 stars outside of the main stream

### 2018-06-19 paper/gd1.tex
polynomial order

To study the global properties of the stream as a function of stream longitude,
we extract stream stars around a second-order polynomial model for the stream
latitude, $\phi_2$, as a function of stream longitude, $\phi_1$.
We find the stream midpoints by computing the median $\phi_2$ in $4^\circ$
windows shifted by $2^\circ$ along $\phi_1$, then fit a parabola to the median
positions to find $\phi_{2, \textrm{track}}(\phi_1)$.
We define the stream region as $\left| \phi_2 - \phi_{2,
\textrm{track}}(\phi_1) \right| < 0.75^\circ$.
\figurename~\ref{fig:track-and-model}, panel (a), shows the high-confidence
stream stars (same as \figurename~\ref{fig:selection}), and the two curved lines
(blue) show the upper and lower boundary of the stream region.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{track_observables.pdf}
\end{center}
\caption{%
Median stream properties computed from the proper motion and CMD filtered GD-1
stars, and the same for a toy model for the stream track.
\textit{Panel (a)}: Sky positions of candidate GD-1 stars.
Lines show a 2nd-order polynomial fit to the median stream track offset by $\pm
0.75^\circ$; the enclosed region is adopted as the nominal stream region.
\textit{Panel (b)}: Sky positions of simulated star particles from a mock stream
model of the GD-1 stream.
\textit{Panel (c)}: Background-subtracted surface-density estimates computed in
successive, overlapping $3^\circ$ windows for both GD-1 data and the model
stream.
\textit{Panel (d)}: Median proper motion along the stream computed in the same
bins as previous panel.
\textit{Panel (e)}: Same as Panel (d), but for proper motion in stream latitude.
}
\label{fig:track-and-model}
\end{figure}

>>>>

To study the global properties of the stream as a function of stream longitude,
we extract stream stars around a fourth-order polynomial model for the stream
latitude, $\phi_2$, as a function of stream longitude, $\phi_1$.
We find the stream midpoints by computing the median $\phi_2$ in $4^\circ$
windows shifted by $2^\circ$ along $\phi_1$, then fit a parabola to the median
positions to find $\phi_{2, \textrm{track}}(\phi_1)$.
We define the stream region as $\left| \phi_2 - \phi_{2,
\textrm{track}}(\phi_1) \right| < 0.75^\circ$.
\figurename~\ref{fig:track-and-model}, panel (a), shows the high-confidence
stream stars (same as \figurename~\ref{fig:selection}), and the two curved lines
(blue) show the upper and lower boundary of the stream region.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{track_observables.pdf}
\end{center}
\caption{%
Median stream properties computed from the proper motion and CMD filtered GD-1
stars, and the same for a toy model for the stream track.
\textit{Panel (a)}: Sky positions of candidate GD-1 stars.
Lines show a \changes{4th}-order polynomial fit to the median stream track offset by $\pm 0.75^\circ$; the enclosed region is adopted as the nominal stream region.
\textit{Panel (b)}: Sky positions of simulated star particles from a mock stream
model of the GD-1 stream.
\textit{Panel (c)}: Background-subtracted surface-density estimates computed in
successive, overlapping $3^\circ$ windows for both GD-1 data and the model
stream.
\textit{Panel (d)}: Median proper motion along the stream computed in the same
bins as previous panel.
\textit{Panel (e)}: Same as Panel (d), but for proper motion in stream latitude.
}
\label{fig:track-and-model}
\end{figure}
